### 2022-01-13 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_metaweb_perspectives@4bfaaf1811e3805832d8dc15ed1acbedf6ef893b 🚀

Graph embedding fig.~\ref{fig:embedding} is a varied family of machine
learning techniques aiming to transform nodes and edges into a vector
space (Arsov \& Mirceva, 2019), usually of a lower dimension, whilst
maximally retaining key properties of the graph (Yan et al., 2005).
Ecological networks are an interesting candidate for the widespread
application of embeddings, as they tend to posess a shared sstructural
backbone (Mora et al., 2018), which hints at structural invariants that
can be revealed a lower dimensions. Indeed, previous work by Eklöf et
al. (2013) suggests that food webs are inherently low-dimensional
objects, and can be adequately represented with less than ten
dimensions. Simulation results by Botella et al. (2022) suggest that
there is no best method to identify architectural similarities between
networks, and that multiple approaches need to be tested and compared to
the network descriptor of interest. This matches with previous, more
general results on graph embedding, which suggest that embedding
algorithm choice matters for the results (Goyal \& Ferrara, 2018).

@@

\begin{minipage}[b]{0.11\columnwidth}\raggedright

@@

\end{minipage} & \begin{minipage}[b]{0.32\columnwidth}\raggedright

@@

\end{minipage} & \begin{minipage}[b]{0.18\columnwidth}\raggedleft

@@

\end{minipage} & \begin{minipage}[b]{0.28\columnwidth}\raggedleft
Species interactions application\strut

@@

\begin{minipage}[t]{0.11\columnwidth}\raggedright

@@

\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
graphs through SVD\strut
\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft

@@

\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedleft

@@

\begin{minipage}[t]{0.11\columnwidth}\raggedright
\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft
\end{minipage} & \begin{minipage}[t]{0.28\columnwidth}\raggedleft
\begin{minipage}[t]{0.11\columnwidth}\raggedright

@@

\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright

@@

\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft

@@

\begin{minipage}[t]{0.11\columnwidth}\raggedright

@@

\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
node embedding\strut
\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft

@@

\end{minipage} & \begin{minipage}[t]{0.32\columnwidth}\raggedright
joint node embedding\strut
\end{minipage} & \begin{minipage}[t]{0.18\columnwidth}\raggedleft

@@

But the popularity of graph embedding techniques in machine learning is
rather more intuitive than the search for structural invariants: while
graphs are discrete objects, machine learning techniques tend to handle
continuous data better. Therefore, bringing a sparse graph into a
continuous, dense vector space (Xu, 2020) opens up a broader variety of
predictive algorithms.

\textbf{TK} Transfer + embedding graf

Rather than directly predicting biological rules (see \emph{e.g.}
Pichler et al., 2020 for an overview), which may be confounded by the
sparse nature of graph data, learning embeddings works in the
low-dimensional space that maximizes information about the network
structure.

The embedding of a network, in a sense, embeds its macro-evolutionary
history, especially as RDPG captures ecological signal (Dalla Riva \&
Stouffer, 2016); at this point,

@@

@@

>>>>

Graph embedding fig.~\ref{fig:embedding} is a varied family of machine
learning techniques aiming to transform nodes and edges into a vector
space (Arsov \& Mirceva, 2019), usually of a lower dimension, whilst
maximally retaining key properties of the graph (Yan et al., 2005).
Ecological networks are an interesting candidate for the widespread
application of embeddings, as they tend to posess a shared sstructural
backbone (Mora et al., 2018), which hints at structural invariants that
can be revealed a lower dimensions. Indeed, previous work by Eklöf et
al. (2013) suggests that food webs are inherently low-dimensional
objects, and can be adequately represented with less than ten
dimensions. Simulation results by Botella et al. (2022) suggest that
there is no best method to identify architectural similarities between
networks, and that multiple approaches need to be tested and compared to
the network descriptor of interest. This matches with previous, more
general results on graph embedding, which suggest that embedding
algorithm choice matters for the results (Goyal \& Ferrara, 2018). In
tbl.~\ref{tbl:methods}, we present a selection of common graph
embeddings methods, alongside examples of their use to predict species
interactions (when they have been used this way).

@@

\begin{minipage}[b]{0.13\columnwidth}\raggedright

@@

\end{minipage} & \begin{minipage}[b]{0.35\columnwidth}\raggedright

@@

\end{minipage} & \begin{minipage}[b]{0.19\columnwidth}\raggedleft

@@

\end{minipage} & \begin{minipage}[b]{0.22\columnwidth}\raggedleft
Application\strut

@@

\begin{minipage}[t]{0.13\columnwidth}\raggedright
\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft
\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedleft
\begin{minipage}[t]{0.13\columnwidth}\raggedright

@@

\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
graph through SVD\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft

@@

\end{minipage} & \begin{minipage}[t]{0.22\columnwidth}\raggedleft

@@

\begin{minipage}[t]{0.13\columnwidth}\raggedright

@@

\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright

@@

\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft

@@

\begin{minipage}[t]{0.13\columnwidth}\raggedright

@@

\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
nodes embedding\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft

@@

\end{minipage} & \begin{minipage}[t]{0.35\columnwidth}\raggedright
joint nodes embedding\strut
\end{minipage} & \begin{minipage}[t]{0.19\columnwidth}\raggedleft

@@

The popularity of graph embedding techniques in machine learning is more
prosaic than the search for structural invariants: graphs are discrete
objects, and machine learning techniques tend to handle continuous data
better. Bringing a sparse graph into a continuous, dense vector space
(Xu, 2020) opens up a broader variety of predictive algorithms, notably
of the sort that are able to predict events as probabilities (Murphy,
2022). Furthermore, the projection of the graph itself is a
representation that can be learned; Runghen et al. (2021), for example,
used a neural network to learn the embedding of a network in which not
all interactions were known, based on nodes metadata. This example has
many parallels in ecology see \ref{fig:prediction}, in which node
metadata can be given by phylogeny or functional traits. Rather than
directly predicting biological rules (see \emph{e.g.} Pichler et al.,
2020 for an overview), which may be confounded by the sparse nature of
graph data, learning embeddings works in the low-dimensional space that
maximizes information about the network structure. This approach is
further justified by the observation, for example, that the
macro-evolutionary history of a network is adequately represented by
some graph embeddings (RDPG; see Dalla Riva \& Stouffer, 2016).

@@

\leavevmode\hypertarget{ref-Murphy2022ProMac}{}%
Murphy, K. P. (2022). \emph{Probabilistic machine learning: An
introduction}. MIT Press. \href{https://probml.ai}{probml.ai}

@@

\leavevmode\hypertarget{ref-Runghen2021ExpNod}{}%
Runghen, R., Stouffer, D. B., \& Dalla Riva, G. V. (2021).
\emph{Exploiting node metadata to predict interactions in large networks
using graph embedding and neural networks}.
\url{https://doi.org/10.1101/2021.06.10.447991}
